Neural fields with different embedding dimensionality can express identical dynamics

### 2024-02-07 paper/equivalence-of-neural-field-dynamics-with-different-embedding-dimensionality.tex
aegument of pointwise convergence

If it exists, we then we define $\alpha = S(v_1, v_2)$ as the pointwise limit of the sequence $\{S^n(v_1, v_2)\}_{n \in \mathbb N}$ (Note: We may define an extension of $S^n$ acting on an arbitrary $(v_1, v_2) \in [0,1]^2$ as $S^n(v_1, v_2) := S^n(v_1^{(n)}, v_2^{(n)})$. This extension is obviously not bijective, but in the $n \to \infty$ limit the finite-$n$ truncation converges, such that the pointwise limit may be a bijection).

>>>>

If it exists, we then we define $\alpha = S(v_1, v_2)$ as the pointwise limit of the sequence $\{S^n(v_1, v_2)\}_{n \in \mathbb N}$ (Note: We may define an extension of $S^n$ acting on an arbitrary $(v_1, v_2) \in [0,1]^2$ as $S^n(v_1, v_2) := S^n(v_1^{(n)}, v_2^{(n)})$. This extension is obviously not bijective, but in the $n \to \infty$ limit the finite-$n$ truncation converges, such that the pointwise limit may be a bijection). In terms of the current formulation, pointwise convergence requires that the least signficiant bits (LSB) of the input be mapped to the LSB of the output, and identically the most significant bits (MSB) of the input be mapped to the MSB of the output [TODO: do we need a proof of this ?]. This ensures that small corrections in the input $\vec{v}$ results in small corrections in the output $\alpha$.
